---
title: "Assignment 1-3"
---

## Introduction

I am examining a dataset of songs by Kishore Kumar

## Setup

```{r}
library(tidyverse)
library(skimr)
library(ggformula)
library(janitor)
```

## Loading the data

```{r}
KishoreKumar1 <- read_csv("../Data/KishoreKumar.csv")
KishoreKumar1
```

## Inspecting the data

```{r}
glimpse(KishoreKumar1)
```

## Data Munging

```{r}
KishoreKumar_modified1 <- KishoreKumar1 %>% 
  janitor::clean_names(case = "snake") %>% 
  mutate(
    movie = as.factor(movie),
    song = as.factor(song),
    gem = as.factor(gem),
    singer_s = as.factor(singer_s),
    music_director_s = as.factor(music_director_s),
    lyrics = as.factor(lyrics)
  )

glimpse(KishoreKumar_modified1)
```

## Data Dictionary

Quantitative Data-

year (dbl): Year in which the song was released

Qualitative Data-

movie (fct): Movie in which the song featured,

song (fct): Name of the song,

gem (fct): Is the song a gem?,

singer_s (fct): Singer/ singers of the song,

music_director_s: Music director/ directors of the song,

lyrics (fct): Lyricists of the song

## Summarising the data

```{r}
skimr::skim(KishoreKumar_modified1)
```

Comments The mean year is around 1973 and there is a standard deviation of around 6 years which means most of the songs were released around that year.

## Visualising the number of songs released per year

```{r}
KishoreKumar_modified1 %>% 
  gf_bar(~ year, color = ~gem, fill = ~gem, alpha = 0.4) %>% 
  gf_labs(x = "Year", y = "Number of songs", title = "Plot 3A: Number of Songs per Year")
```

Comments MOst of the songs were released in 1973. The release of songs increased gradually from the 1950s, peaked in the 70s and started decreasing after 1973.

## Visualising the number of songs in which Kishore Kumar collaborated with each music director

```{r}
KishoreKumar_modified1 %>%
  dplyr::count(music_director_s) %>%
  gf_col(music_director_s ~ n, color = "blue", fill = "lightblue") %>%
  gf_labs(x = "Number of Songs", y = "Music Director", title = "Plot 3B: Music Directors Collaborating with Kishore Kumar")
```

Comments The chart shows that Kishore Kumar collaborated the most with R.D. Burman and also collaborated a lot with Laxmikant Pyarelal, Kalyanji Anandji, S. D. Burman and Shankar Jaikishen.

## Visualising the number of songs in which Kishore Kumar collaborated with each lyricist

```{r}
KishoreKumar_modified1 %>%
  dplyr::count(lyrics) %>%
  gf_col(lyrics ~ n, color = "orange", fill = "orchid") %>%
  gf_labs(x = "Number of Songs", y = "Lyricists", title = "Plot 3C: Lyricists Collaborating with Kishore Kumar")
```

Comments The chart shows that Kishore Kumar collaborated the most with Anand Bakshi and also collaborated a lot with Majrooh Sultanpuri, Rajendra Krishan, Sahil Ludhianvi, Indeevar, Gulshan Bawra, Hasrat Jaipuri and Gulzar
